---
title: "R Notebook for visualizing predictions"
output: html_notebook
---

Vidualize

```{r}
library(raster) 
library(rgdal)
# ASO
aso <- raster('data/ASO_3M_SD_USCATE_20180528_binary_merged.tif') 
# GPredicted
mlp <- raster('data/20180528_181108_1025_3B_AnalyticMS_SR_clip_merged.tif')
```

Print the variables to check. E.g.
```{r}
aso
```



```{r}
mlp
```


Its the same

Image information and statistics
The below shows how you can access various properties from a Raster* object (this is the same for any raster data set).
# Do the bands have the same extent, number of rows and columns, projection, ˓→resolution, and origin

```{r}
compareRaster(aso,mlp)
```


```{r}
crs(aso)
```

```{r}
crs(mlp)
```

number of cells, spatial res and number of bands

```{r}
ncell(mlp)
## [1] 18880512
dim(mlp)
## [1] 3073 6144    1
# spatial resolution
res(mlp)
## [1] 2.145767e-05 1.685681e-05
# Number of bands
nlayers(mlp)
#1
```

```{r}
ncell(aso)
## [1] 18880512
dim(aso)
## [1] 3073 6144    1
# spatial resolution
res(aso)
## [1] 2.145767e-05 1.685681e-05
# Number of bands
nlayers(aso)
#1
```

You can create a RasterStack (an object with multiple layers) from the existing RasterLayer (single band) objects.
```{r}

s <- stack(mlp,aso)
```

plot

```{r}
par(mfrow = c(1,1))
plot(aso, main = "ASO")
plot(mlp, main = "ML P")
```


stack preduction and ASO

```{r}
 twoB<- stack(aso,mlp)
plotRGB(twoB, axes = TRUE, stretch = "lin", main = "Pred and ASO")

```
A scatterplot matrix can be helpful in exploring relationships between raster layers. This can be done with the pairs() function of the raster package

```{r}
pairs(twoB[[1:2]], main = "ASO versus ML P")
```


We are underprecting no-snow, and we are over predicting snow
